Forschungsprojekt

### 2020-08-10 documentation/paper/galois.tex
little paper work

Galois \cite{Galois} is a general purpose library designed for parallel programming. The Galois system supports fine grain tasks, allows for autonomous, speculative execution of these tasks and grants control over the task scheduling policies to the application. It also simplifies the implementation of parallel applications by providing an implicitly parallel unordered-set iterator.\\
For graph analytics purposes a topology aware work stealing scheduler, a priority scheduler and a library of scalable data structures have been implemented. Galois includes applications for for many graph analytics problems, among these are single-source shorthest-paths (sssp) and pagerank. Both of these applications can be executed in shared memory systems and due to the Gluon integration in a distributed environment.\\
Gluon \cite{vertGalois} reduces the communication overhead needed in distributed systems for graph analysis by exploiting structural and temporal invariants.

>>>>

Galois\cite{Galois} is a general purpose library designed for parallel programming. The Galois system supports fine grain tasks, allows for autonomous, speculative execution of these tasks and grants control over the task scheduling policies to the application. It also simplifies the implementation of parallel applications by providing an implicitly parallel unordered-set iterator.

For graph analytics purposes a topology aware work stealing scheduler, a priority scheduler and a library of scalable data structures have been implemented. Galois includes applications for for many graph analytics problems, among these are single-source shorthest-paths (sssp), breath-first-search (bfs) and pagerank. For most of these applications Galois offers a huge amount of algorithms to perform these analytics problems and many setting options, like the amount of threads used or policies for splitting the graph. All of these applications can be executed in shared memory systems and due to the Gluon integration in a distributed environment.

Gluon\cite{vertGalois} is a framework written by the Galois team as a middleware to write distributed systems for graph analysis. It reduces the communication overhead needed in distributed by exploiting structural and temporal invariants.

The code of Gluon is embedded into the project of Galois and already integrated with it. It is possible to integrate Gluon with other frameworks too, which the Galois team showed in their paper\cite{vertGalois}.

### 2020-08-10 documentation/paper/graphFormats.tex
little paper work

\subsubsection{EdgeList}
The EdgeList format is probably the easiest to understand and is one of the most commonly used in the online graph repositories. The directed eges $(s_1,t_1),(s_2,t_2),\ldots$ are represented in the following way.
\begin{align*}
	&s_1,t_1\\
	&s_2,t_2\\
	&\quad\vdots\\
	&s_m,t_m
\end{align*}

@@

We found that Gemini requires the following input format
\begin{equation*}
	s_1t_1w_1s_2t_2w_2\ldots
\end{equation*}
where $s_i,t_i$ have \texttt{uint32} ?? data type and the weights are \texttt{float32}. 
Gemini will derive the number of edges from the file size, so there is no file header or anything similar allowed.

>>>>

\subsubsection{EdgeList}
The EdgeList format is probably the easiest to understand and is one of the most commonly used in the online graph repositories. The directed eges $(s_1,t_1),(s_2,t_2),\ldots$ or $(s_1,t_1, w_1),(s_2,t_2, w_2),\ldots$ are represented in the following way.
\begin{align*}
  &s_1\ \ t_1\ \ w_1\\
  &s_2\ \ t_2\ \ w_m\\
	&\quad\vdots\\
  &s_m\ \ t_m\ \ w_m
\end{align*}
The weights are optional, everything is ASCI encoded and the inline delimiter is a variable amount of any whitespace.

@@

We found that Gemini requires the following input format
\begin{equation*}
	s_1t_1w_1s_2t_2w_2\ldots
\end{equation*}
where $s_i,t_i$ have \texttt{uint32} data type and the optional weights are \texttt{float32}.
Gemini will derive the number of edges from the file size, so there is no file header or anything similar allowed.
